neonstore: a local, provenance-aware workflow for NEON data

### 2021-03-12 paper/paper.Rmd

---
title: "taxadb: A High-Performance Local Taxonomic Database Interface"
author:
  - name: "Carl Boettiger"
    affiliation: ucb
  - name: "Christine Laney"
    affiliation: neon
  - name: "Quinn Thomas"
    affiliation: vt
address:
  - code: ucb
    address: "Dept of Environmental Science, Policy, and Management, University of California Berkeley, Berkeley CA 94720-3114, USA"
  - code: neon
    address: "NEON"
  - code: vt
    address: "Virginia Tech"
abstract: |
  The National Ecological Observatory Network
journal: "TBD"
date: "`r Sys.Date()`"
bibliography: refs.bib
layout: 3p
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output: rticles::elsevier_article
---

@@

The National Ecological Observatory Network (NEON) provides open access ecological data as 181 (active and planned) data products at 81 (permanent and relocatable) sites throughout the United States.  The `neonstore` R package seeks to provide quick, convenient access and persistent storage of NEON data files.  `neonstore` design emphasizes simplicity and data provenance. Here, we describe the design, use, and rationale for the package.

>>>>

---
title: "neonstore: a local, provenance-aware workflow for NEON data"
author:
  - name: "Carl Boettiger"
    affiliation: ucb
  - name: "Quinn Thomas"
    affiliation: vt
  - name: "Christine Laney"
    affiliation: neon
  - name: "Claire Lunch"
    affiliation: neon
address:
  - code: ucb
    address: "Dept of Environmental Science, Policy, and Management, University of California Berkeley, Berkeley CA 94720-3114, USA"
  - code: neon
    address: "NEON"
  - code: vt
    address: "Virginia Tech"
abstract: |
  The National Ecological Observatory Network
journal: preprint
date: "`r Sys.Date()`"
bibliography: refs.bib
layout: 3p
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output: rticles::elsevier_article
---

@@

The National Ecological Observatory Network (NEON) represents an important resource and a major investment in data collection infrastructure needed to address many of the grand challenges facing envionmental science [@NAS_NEON; @NAS_GRAND].

provides open access ecological data as 181 (active and planned) data products at 81 (permanent and relocatable) sites throughout the United States.  The `neonstore` R package seeks to provide quick, convenient access and persistent storage of NEON data files.  `neonstore` design emphasizes simplicity and data provenance. Here, we describe the design, use, and rationale for the package.
